---
title: 'M2-8: Natural Language Processing: Case Studies (R)'
author: "Daniel S. Hain (dsh@business.aau.dk)"
date: "Updated `r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
    theme: flatly
---

```{r setup, include=FALSE}
### Generic preamble
Sys.setenv(LANG = "en") # For english language
options(scipen = 5) # To deactivate annoying scientific number notation
set.seed(1337) # To have a seed defined for reproducability

### Knitr options
if (!require("knitr")) install.packages("knitr"); library(knitr) # For display of the markdown
knitr::opts_chunk$set(warning=FALSE,
                     message=FALSE,
                     fig.align="center"
                     )

### Install packages if necessary
if (!require("pacman")) install.packages("pacman") # package for loading and checking packages :)
pacman::p_load(tidyverse, # Standard datasciewnce toolkid (dplyr, ggplot2 et al.)
               magrittr, # For advanced piping (%>% et al.)
               igraph, # For network analysis
               tidygraph, # For tidy-style graph manipulation
               ggraph, # For ggplot2 style graph plotting
               Matrix, # For matrix tooling
               bibliometrix, # for bibliometric analysis
               data.table # for fast data manipulation
               )
```

In this session, you will learn:

1. What are alternative ways to create network structures.
2. What are different options to visualize networks and highlight properties.
3. How to analyse multi-modal networks.




















## Your turn
Please do **Exercise 1** in the corresponding section on `Github`. This time you are about to do your own bibliographic analysis!

# Endnotes

### References

### More info
You can find more info about:

* `tidygraph` [here](https://tidygraph.data-imaginist.com/)


### Session info
```{r}
sessionInfo()
```
